Results

### 2025-07-27 notebooks/000_data.qmd
update

```{julia}
let tmin = DateTime("2021-01-15")
    tvars = (
        [Wind.V_GSE_3DP, Wind.V_GSE_K0],
        [Wind.n_p_K0, Wind.n_p_3DP, Wind.n_p_nonlin],
    )
    tplot(tvars, tmin, tmin + Hour(3))
end
```

>>>>

```{julia}
let tmin = DateTime("2021-01-15")
    tvars = (
    # [Wind.V_GSE_3DP, Wind.V_GSE_K0],
        [
        unitify("1/cm^3") ∘ SpeasyProduct("WI_K0_SWE/Np"; labels=["Proton"]),
        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=["Proton (3DP, PESA Low)"]),
        SpeasyProduct("WI_H1_SWE/Proton_Np_nonlin", labels=["Proton (non-linear fitting)"]),
        SpeasyProduct("WI_H1_SWE/Alpha_Na_nonlin", labels=["Alpha (non-linear fitting)"]),
        Wind.n_e
    ],
    )
    tplot(tvars, tmin, tmin + Hour(3))
end
```

### 2025-07-27 notebooks/00_index.qmd
feat: add alpha
update

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: set_meta, set_meta!
using PartialFunctions

@@

```{julia}
using DimensionalData
Tp = PSP.read_proton_temperature(7:8)
Te = PSP.read_electron_temperature()

@@

add_temp_anisotropy!(psp_df, Tp, Te)
compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
```

```{julia}
function plot_candidate(f, event, config, toffset=Second(0); add_J=false, kwargs...)
    tmin, tmax = event.t_us_ds
    t0 = tmin - toffset
    t1 = tmax + toffset

    B_product = config["B"]
    V_product = config["V"]

    B = B_product(t0, t1) |> set_meta!(; ylabel="B", labels=𝑳.B_RTN)
    V = V_product(t0, t1) |> set_meta!(; ylabel="V", labels=𝑳.V_RTN)
    n = config["n"](t0, t1)

    B_mva = mva(B, B) |> set_meta(; labels=𝑳.B_LMN)
    Va = Alfven_velocity_ts(B_mva, n) .|> u"km/s" |> set_meta(; labels=𝑳.Va_LMN, ylabel="V")
    V_mva = mva(V, B) |> set_meta(; labels=𝑳.V_LMN)

    result = [tnorm_combine(B_mva), tsubtract(V_mva), tsubtract(Va)]

    if add_J
        J = hcat(current_density(B_mva, V_mva)...) |> set_meta(; labels=𝑳.J, ylabel="J")
        push!(result, J)
    end

    f = tplot(f, result; kwargs...)
    tlines!(f, [tmin, tmax])
    result
end

f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.v_l_ratio
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

@@

```{julia}
using Speasy
using SPEDAS: tnorm_combine, tplot, DataSet
using DimensionalData
using CairoMakie
# using GLMakie
using Statistics
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set

import Discontinuity.AlgebraOfGraphics as AoG

@@

function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
    v_l_ratio_ts, n1 = _get_vl_ratio_ts(df, :v_l_ratio, dt)
    v_l_ratio_Λ_ts, n2 = _get_vl_ratio_ts(df, :v_l_ratio_Λ, dt)
    vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
    return vl_ratio_ts, n1
end
```

@@

function modify_faxs_base!(faxs)
    B_ax = faxs.axes[1]
    B_ax.ylabel[] = 𝒀.B
    V_ax = faxs.axes[3]
    V_ax.ylabel[] = 𝒀.V
    n_ax = faxs.axes[2]
    n_ax.yscale[] = identity
    n_ax.ylabel[] = 𝒀.n
end

function modify_faxs_vl!(faxs)
    T_ax = faxs.axes[end-3]
    T_ax.ylabel[] = "T (eV)"

    R_ax = faxs.axes[end-1]
    ylims!(R_ax, 0.09, 0.85)

    β_ax = faxs.axes[end]
    β_ax.yscale[] = log10
    β_ax.ylabel[] = "β"
    ylims!(β_ax, 8e-2, 4e1)
end

for enc in 7:9
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)

@@

    tvars_psp = (psp_B, psp_n, psp_V)
    tvars_wind = (wind_B, wind_n, wind_V)

@@

    if plot_vl_ratio
        fname = "overview-vl-$enc"

        B = set_meta!(PSP.B_1MIN(tmin_psp, tmax_psp); labels=𝑳.B_RTN)
        V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
        n = PSP.n_spi(tmin_psp, tmax_psp) |> tvec
        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false) |> tvec

        B_mag = tnorm(B)
        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)

        T = rebuild(T; metadata=(; labels=[L"T_p"]))

        psp_v_l_ratio_ts, psp_count = get_vl_ratio_ts(psp_df)
        tvars_psp = (B_mag, n, tnorm(V), tmean.((T, Tp, Te), Minute(8)), psp_count, psp_v_l_ratio_ts, β)

        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind; add_unit=false)
        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind; add_unit=false)
        add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
        compute_anisotropy_params!(wind_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))

        B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
        V = wind_V(tmin_wind, tmax_wind)
        n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind; add_unit=false) |> tsort; metadata=(; labels=[L"T_p"]))
        B_mag = tnorm(B)
        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)

        wind_v_l_ratio_ts, wind_count = get_vl_ratio_ts(wind_df)
        tvars_wind = (B_mag, n, tnorm(tsort(V)), [T, Wind_Tp2, Wind_Te2], wind_count, wind_v_l_ratio_ts, β)
    end

    faxs = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 1]; labels, open="(a.", padding)
    faxs = tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 2]; labels, open="(b.", padding)

    # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")

@@

    # f = Figure(; size=(1200, 600))
    # plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    # add_labels!(f[1, 1]; labels, open="(a.")
    # tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 2]; labels, open="(b.")
    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
    # easy_save("overview-$enc-all")
end
```

@@

```{julia}
psp_df_taus = map([8, 16, 32]) do tau
    psp_config["tau"] = tau
    df = PSPAnisotropy.produce(psp_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([8, 16, 32]) do tau
    wind_config["tau"] = tau
    df = PSPAnisotropy.produce(wind_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```

```{julia}
f = Figure()
axR1 = Axis(f[1, 1])
axn1 = Axis(f[2, 1])
for (i, df) in enumerate(psp_df_taus)
    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
    lines!(axR1, v_l_ratio_ts)
    lines!(axn1, n)
end

axR2 = Axis(f[1, 2])
axn2 = Axis(f[2, 2])
for (i, df) in enumerate(wind_df_taus)
    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
    lines!(axR2, v_l_ratio_ts)
    lines!(axn2, n)
end

ylims!.((axR1, axR2), 0.2, 0.8)
ylims!.((axn1, axn2), 11, 121)
easy_save("vl_ratio-tau")
f
```

>>>>

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: set_meta, set_meta!
using Beforerr: _theme_legend, easy_save
using PartialFunctions

@@

```{julia}
using DimensionalData

@@

function compute_PSP_anisotropy_params!(psp_df)
    Tp = PSP.read_proton_temperature(7:8)
    Te = PSP.read_electron_temperature()
    add_temp_anisotropy!(psp_df, Tp, Te)
    compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
end

function compute_Wind_anisotropy_params!(df, tmin, tmax)
    Wind_Tp2 = Wind.pTemp_T2(tmin, tmax; add_unit=false)
    Wind_Te2 = Wind.eTemp_T2(tmin, tmax; add_unit=false)
    add_temp_anisotropy!(df, Wind_Tp2, Wind_Te2, Minute(2))
    compute_anisotropy_params!(df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
end
```

```{julia}
f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

@@

```{julia}
using Speasy
using SPEDAS: tnorm_combine, tplot, DataSet
using DimensionalData
using CairoMakie
# using GLMakie
using Statistics
using PartialFunctions
using Unitful
using SPEDAS.SpaceDataModel: set, extend, @set

import AlgebraOfGraphics as AoG

@@

function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
    v_l_ratio_ts, n1 = get_vl_ratio_ts(df, :V_l_ratio, dt)
    v_l_ratio_Λ_ts, n2 = get_vl_ratio_ts(df, :V_l_ratio_Λ, dt)
    vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
    return vl_ratio_ts, n1
end
```

```{julia}
function modify_faxs_base!(faxs)
    B_ax = faxs.axes[1]
    B_ax.ylabel[] = 𝒀.B
    V_ax = faxs.axes[3]
    V_ax.ylabel[] = 𝒀.V
    n_ax = faxs.axes[2]
    n_ax.yscale[] = identity
    n_ax.ylabel[] = 𝒀.n
end

function modify_faxs_vl!(faxs)
    i = 1
    T_ax = faxs.axes[end-3-i]
    T_ax.ylabel[] = "T (eV)"

    R_ax = faxs.axes[end-2-i]
    ylims!(R_ax, 0.09, 0.85)

    β_ax = faxs.axes[end-i]
    β_ax.yscale[] = log10
    ylims!(β_ax, 8e-2, 4e1)

    A_He_ax = faxs.axes[end]
    A_He_ax.yscale[] = identity
    A_He_ax.ylabel[] = L"A_{\text{He}} (%)"
    ylims!(A_He_ax, 0, 8)
end

f = Figure(; size=(800, 600))
# faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...)
modify_faxs_vl!(faxs)
f
```

```{julia}
let tmin = tmin_psp, tmax = tmax_psp
    f = Figure(; size=(800, 600))

    faxs = plot_Wind(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(wind_df)...)
    f
end
```

@@

for enc in 7:7
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)

@@

@@

    if plot_vl_ratio
        fname = "overview-vl-$enc"
        faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
        modify_faxs_base!(faxs)
        plot_vl_ratio && modify_faxs_vl!(faxs)

        compute_Wind_anisotropy_params!(wind_df, tmin_wind, tmax_wind)
        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind, get_vl_ratio_ts(wind_df)...; legend)
        modify_faxs_base!(faxs)
        plot_vl_ratio && modify_faxs_vl!(faxs)
    end

    add_labels!(f[1, 1]; labels, open="(a.", padding)
    add_labels!(f[1, 2]; labels, open="(b.", padding)

@@

    # tvars_psp = (psp_B, psp_n, psp_V)
    # tvars_wind = (wind_B, wind_n, wind_V)
    # f = Figure(; size=(1200, 600))
    # plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    # add_labels!(f[1, 1]; labels, open="(a.")
    # tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 2]; labels, open="(b.")
    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
    # easy_save("overview-$enc-all")
end
```

@@

```{julia}
psp_df_taus = map([2, 4, 8, 16, 32]) do tau
    psp_config["tau"] = tau
    df = PSPAnisotropy.produce(psp_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([2, 4, 8, 16, 32]) do tau
    wind_config["tau"] = tau
    df = PSPAnisotropy.produce(wind_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```

Check examples

```{julia}
f = Figure(; size=(1200, 800))
# let df = psp_df_taus[1], config = psp_config
begin
    df = @subset(wind_df_taus[1], :index_std .> 4)
    config = wind_config
    event = filter_low_mva_quality(df)[5, :]
    fax, res_psp = plot_candidate(f[1, 1], event, config, Second(10))
    plot_var_info!(fax, event)
    @info "v_l_ratio" event.V_l_ratio event.V_l_ratio_max
end
f
```

```{julia}
f = Figure()
axR1 = Axis(f[1, 1])
axn1 = Axis(f[2, 1])
filter_func = df -> @subset(df, :index_std .> 2)

for (i, df) in enumerate(psp_df_taus)
    v_l_ratio_ts, n = get_vl_ratio_ts(filter_func(df), :V_l_ratio_max)
    lines!(axR1, v_l_ratio_ts)
    lines!(axn1, n)
end

axR2 = Axis(f[1, 2])
axn2 = Axis(f[2, 2])
for (i, df) in enumerate(wind_df_taus)
    v_l_ratio_ts, n = get_vl_ratio_ts(filter_func(df), :V_l_ratio_max)
    lines!(axR2, v_l_ratio_ts)
    lines!(axn2, n)
end

ylims!.((axR1, axR2), 0, 0.8)
# ylims!.((axn1, axn2), 0, 121)
easy_save("vl_ratio-tau")
f
```
